Predicting tree failure likelihood for utility risk mitigation via a novel convolutional neural network

### 2021-02-17 docs/manuscript/manuscript.tex
Updates from Overleaf

We can apply cut-out (occluding portions of the image) for improved performance \cite{devries2017improved}. Also, it has been shown that training with lower resolution improves performance on higher resolution test images \cite{touvron2019fixing}.

@@

 \begin{tabular}{@{}llr r@{}}

@@

& & \multicolumn{2}{c}{\bf Resolution}\\
\textbf{Scenario}   & \textbf{Hyperparameters} & 64                & 128               \\ \midrule
PrPo\_Im   & activation\_1   & relu              & tanh              \\
   & activation\_2   & relu              & relu              \\
   & dropout\_1      & 0.1               & 0.25              \\
   & dropout\_2      & 0.3               & 0.35              \\
   & kernel\_size    & 7                 & 5                 \\
   & learning\_rate  & \num{0.000102956216062} & \num{0.000109137476524} \\
   & units\_1        & 480               & 384               \\
   & units\_2        & 448               & 256               \\
Pr\_Im     & activation\_1   & relu              & relu              \\
      & activation\_2   & relu              & relu              \\
      & dropout\_1      & 0.1               & 0.1               \\
     & dropout\_2      & 0.3               & 0.3               \\
      & kernel\_size    & 7                 & 7                 \\
      & learning\_rate  & \num{0.000102956216062} & \num{0.000102956216062} \\
      & units\_1        & 480               & 480               \\
      & units\_2        & 448               & 448               \\
Pr\_PoIm   & activation\_1   & relu              & relu              \\
   & activation\_2   & tanh              & relu              \\
   & dropout\_1      & 0.25              & 0.1               \\
   & dropout\_2      & 0.3               & 0.3               \\
   & kernel\_size    & 7                 & 7                 \\
   & learning\_rate  & \num{0.000175822328104} & \num{0.000102956216062} \\
   & units\_1        & 128               & 480               \\
   & units\_2        & 320               & 448               \\
Pr\_Po\_Im & activation\_1   & relu              & tanh              \\
  & activation\_2   & tanh              & relu              \\
  & dropout\_1      & 0.25              & 0.25              \\
  & dropout\_2      & 0.3               & 0.35              \\
  & kernel\_size    & 7                 & 5                 \\
  & learning\_rate  & \num{0.000175822328104} & \num{0.000109137476524} \\
  & units\_1        & 128               & 384               \\
  & units\_2        & 320               & 256              \\\bottomrule

>>>>

% We can apply cut-out (occluding portions of the image) for improved performance \cite{devries2017improved}. Also, it has been shown that training with lower resolution improves performance on higher resolution test images \cite{touvron2019fixing}.

@@

% \usepackage{multirow}
\begin{tabular}{@{}lllll@{}}

@@

\multirow{2}{*}{\textbf{Scenario}} & \multirow{2}{*}{\textbf{Hyperparameters}} & \multicolumn{3}{c}{\textbf{Resolution}} \\ \cmidrule(l){3-5} 
                            &                & 64                & 128               & 224               \\ \midrule
\multirow{8}{*}{PrPo\_Im}   & activation\_1  & relu              & tanh              & relu              \\
                            & activation\_2  & relu              & relu              & relu              \\
                            & dropout\_1     & 0.1               & 0.25              & 0.1               \\
                            & dropout\_2     & 0.3               & 0.35              & 0.3               \\
                            & kernel\_size   & 7                 & 5                 & 7                 \\
                            & learning\_rate & \num{0.000102956216062} & \num{0.000109137476524} & \num{0.000102956216062} \\
                            & units\_1       & 480               & 384               & 480               \\
                            & units\_2       & 448               & 256               & 448               \\\midrule
\multirow{8}{*}{Pr\_Im}     & activation\_1  & relu              & relu              & relu              \\
                            & activation\_2  & relu              & relu              & relu              \\
                            & dropout\_1     & 0.1               & 0.1               & 0.1               \\
                            & dropout\_2     & 0.3               & 0.3               & 0.3               \\
                            & kernel\_size   & 7                 & 7                 & 7                 \\
                            & learning\_rate & \num{0.000102956216062} & \num{0.000102956216062} & \num{0.000102956216062} \\
                            & units\_1       & 480               & 480               & 480               \\
                            & units\_2       & 448               & 448               & 448               \\\midrule
\multirow{8}{*}{Pr\_PoIm}   & activation\_1  & relu              & relu              & relu              \\
                            & activation\_2  & tanh              & relu              & tanh              \\
                            & dropout\_1     & 0.25              & 0.1               & 0.2               \\
                            & dropout\_2     & 0.3               & 0.3               & 0.15              \\
                            & kernel\_size   & 7                 & 7                 & 7                 \\
                            & learning\_rate & \num{0.000175822328104} & \num{0.000102956216062} & \num{0.000114656409879} \\
                            & units\_1       & 128               & 480               & 416               \\
                            & units\_2       & 320               & 448               & 416               \\
\multirow{8}{*}{Pr\_Po\_Im} & activation\_1  & relu              & tanh              & relu              \\\midrule
                            & activation\_2  & tanh              & relu              & relu              \\
                            & dropout\_1     & 0.25              & 0.25              & 0.1               \\
                            & dropout\_2     & 0.3               & 0.35              & 0.3               \\
                            & kernel\_size   & 7                 & 5                 & 7                 \\
                            & learning\_rate & \num{0.000175822328104} & \num{0.000109137476524} & \num{0.000102956216062} \\
                            & units\_1       & 128               & 384               & 480               \\
                            & units\_2       & 320               & 256               & 448               \\ \bottomrule
